Curation of NYC 311 Request Open Data

### 2023-06-09 talk/slides.Rmd
went through slides with David

```{r read}
d311 <- read.csv("../data/311_202303.csv", header = TRUE)
names(d311) <- makeColNamesUserFriendly(names(d311))
dim(d311)
tail(names(d311))
```

@@

## Invalid Data: Created/Closed Date
```{r date}
t1 <- strptime(d311$closed_date, format = '%m/%d/%Y %I:%M:%S %p')
t0 <- strptime(d311$created_date, format = '%m/%d/%Y %I:%M:%S %p')
tt <- as.numeric(difftime(t1, t0, units =  "secs"))
badTime <- subset(d311, tt <= 0,
                  select = c("created_date", "closed_date", "agency"))

@@

## Invalid Data: Borough
```{r borough}
validBorough <- c("BRONX", "BROOKLYN", "MANHATTAN", "QUEENS", "STATEN ISLAND")
badBorough <- subset(d311, ! borough %in% validBorough,
                     select = c("borough", "agency"))
head(table(badBorough$agency))
```

@@

## Invalid Data: Open Data Channel
```{r channel}
validChannel <- c("MOBILE", "ONLINE", "PHONE")
badChannel_type <- subset(d311, ! open_data_channel_type %in% validChannel,
                          select = c("open_data_channel_type", "agency"))
head(table(badChannel_type$agency))
```

@@

##  Cross Street and Intersection Street (cont'd)
```{r extra_space}
## after removing extra spaces, most of them are the same
dupXStreets <-subset(
    d311, gsub(" ", "", cross_street_1) ==
          gsub(" ", "", intersection_street_1),
    select = c("cross_street_1", "intersection_street_1", "agency"))
head(dupXStreets)
```

@@

## Less-Efficient Storage: Download File Size
```{r storage}
## code borough by integer
object.size(d311$borough_boundaries)
object.size(d311$borough)

@@

@@

+ Validity check 
    - date (logical check)
    - legitimate values 
	- descriptive fields (drop-down menu, possibly multi-step)
    - missing value: coding; validity
    - computed fields in the dictionary
+ Efficiency
    - Eliminate redundant columns
    - Reduce storage with no information loss
+ Feedback: 
    - open review for open data
	- interaction with the maintenance team

## Discussion

+ something
+ something else

>>>>

```{r read}
d311 <- read.csv("../data/311_202303by202305.csv", header = TRUE)
names(d311) <- makeColNamesUserFriendly(names(d311))
dim(d311)
tail(names(d311))
```

@@

## Invalid Data: Created/Closed Date
```{r date}
t1 <- strptime(d311$closed_date, format = '%m/%d/%Y %I:%M:%S %p')
t0 <- strptime(d311$created_date, format = '%m/%d/%Y %I:%M:%S %p')
tt <- as.numeric(difftime(t1, t0, units =  "day"))
badTime <- subset(d311, tt <= 0,
                  select = c("created_date", "closed_date", "agency"))

@@

## Invalid Data: Borough
```{r borough}
validBorough <- c("BRONX", "BROOKLYN", "MANHATTAN", "QUEENS", "STATEN ISLAND",
                  "Unspecified")
badBorough <- subset(d311, ! borough %in% validBorough,
                     select = c("borough", "agency"))
head(table(badBorough$agency))
head(table(subset(d311, borough == "Unspecified")$agency))
```

@@

## Invalid Data: Open Data Channel
```{r channel}
validChannel <- c("MOBILE", "ONLINE", "PHONE", "OTHER")
badChannel_type <- subset(d311, ! open_data_channel_type %in% validChannel,
                          select = c("open_data_channel_type", "agency"))
head(table(badChannel_type$agency)) ## UNKNOWN
```

@@

##  Cross Street and Intersection Street (cont'd)
```{r extra_space}
## after removing extra spaces, most of them are the same
dupXStreets <- subset(
    d311, gsub(" ", "", cross_street_1) ==
          gsub(" ", "", intersection_street_1),
    select = c("cross_street_1", "intersection_street_1", "agency"))
nrow(dupXStreets)
head(dupXStreets)
```

@@

## Less-Efficient Storage: Memory
```{r storage}
## code borough by integer
object.size(d311$borough_boundaries)
object.size(d311$borough)

@@

## Less-Efficient Storage: Disk
```{r storage-disk}
write.csv(subset(
    d311, select = -c(park_borough, borough_boundaries, location,
                      intersection_street_1, intersection_street_2,
                      agency_name)),
    quote=FALSE, row.names = FALSE,
    file = "../data/311_202303_smaller.csv")

(newsize <- file.size("../data/311_202303_smaller.csv"))
(oldsize <- file.size("../data/311_202303by202305.csv"))
(oldsize - newsize) / oldsize
```

@@

+ Improve dictionary
    - Code categorical variables (e.g., agency) 
	- Code descriptive fields (e.g., complain type; vehicle type)
    - Make the descriptions informative (e.g., zip code)
+ Impose validity check
    - date (logical check)
    - legitimate values 
	- descriptive fields (drop-down menu, possibly multi-step)
    - missing value: coding; validity
+ Improve data storage/transportation efficiency
    - Eliminate redundant columns
    - Reduce storage with no information loss
+ Feedback: 
    - Open review for open data
	- Interaction with the maintenance team
